data-exploration

### 2022-04-25 scripts/data-exploration.Rmd
aic tables

model <- lm(delay_log ~ day + incident + hour, data = df2015) # TODO: use hour as variable but can't figure it out above lol
anova(model) # show results
summary(model)
plot(model)

two_way_day_incident <- aov(delay_log ~ day + incident, data = df)
two_way_day_hour <- aov(delay_log ~ day + hour, data = df2015)
two_way_incident_hour <- aov(delay_log ~ hour + incident, data = df2015)

interaction_day_incident <- aov(delay_log ~ day * incident, data = df2015)
interaction_day_hour <- aov(delay_log ~ day * hour, data = df2015)
interaction_incident_hour <- aov(delay_log ~ hour * incident, data = df2015)

combine_day_incident_plus_hour <- aov(delay_log ~ day * incident + hour, data = df2015)
combine_incident_hour_plus_day <- aov(delay_log ~ day + incident * hour, data = df2015)
combine_day_hour_plus_incident <- aov(delay_log ~ day * hour + incident, data = df2015)

@@

aictab(model.set, modnames = model.names)
```
```{r}
summary(combine_incident_hour_plus_day)
TukeyHSD(combine_incident_hour_plus_day)
```

>>>>

length(df[, day])
length(df[, delay_log])

model <- lm(delay_log ~ day + incident + hour, data = df2015) 
anova(model) # show results
summary(model)
plot(model)

two_way_day_incident <- aov(delay_log ~ day + incident, data = df) 
two_way_day_hour <- aov(delay_log ~ day + hour, data = df)
two_way_incident_hour <- aov(delay_log ~ hour + incident, data = df)

interaction_day_incident <- aov(delay_log ~ day * incident, data = df)
interaction_day_hour <- aov(delay_log ~ day * hour, data = df)
interaction_incident_hour <- aov(delay_log ~ hour * incident, data = df)

combine_day_incident_plus_hour <- aov(delay_log ~ day * incident + hour, data = df)
combine_incident_hour_plus_day <- aov(delay_log ~ day + incident * hour, data = df)
combine_day_hour_plus_incident <- aov(delay_log ~ day * hour + incident, data = df)

@@

aic_table <- aictab(model.set, modnames = model.names)
aic_table <- data.table(aic_table)

saveRDS(aic_table, file = '../inputs/aic-table.RDS')
```
```{r}
summary(combine_incident_hour_plus_day)
TukeyHSD(combine_incident_hour_plus_day)
```
